Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-24 awipev-CO2.Rmd
Figure data availability finalized

+ 1: good data
+ 3: failing the date and time test
+ 4: data not usable according to manufacturer
+ 7: failing the regional range test 
+ 12: failing the spike test (NAs from despike)
+ 13: failing the gradient test
+ 15: instrument not deployed or operated
+ 16: acid flush
+ 99: failing the final visual inspection

@@

    + 1: good data
    + 3: impossible date and time test
    + 4: data not usable according to manufacturer (flush mode, zero mode, calibration mode...) 
    + 6: failing the manufacturer range test (not used)
    + 7: failing the regional range test 
    + 12: failing the spike test (NAs from despike)
    + 13: failing the gradient test
    + 15: the instrument was not deployed or operated
    + 99: failing the final visual inspection of the data.

```{r data availability, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
# function to express the number of quality flag in pefrcent for each variable
# qflag <- function(x, ...) {
#   tmp <- summary(as.factor(x))*100/length(x)
#   return(tmp)
# }
d <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_minute.rds")) %>%
dplyr::select(datetime, c(pco2_corr_qf, sal_fb_qf, sal_insitu_ctd_qf, 
                          temp_fb_qf, temp_insitu_11m_qf, ph_dur_qf, phINT_qf))

s1 <- summary(as.factor(d$pco2_corr_qf))*100/length(d$pco2_corr_qf)
s2 <- summary(as.factor(d$sal_fb_qf))*100/length(d$sal_fb_qf)
s3 <- summary(as.factor(d$sal_insitu_ctd_qf))*100/length(d$sal_insitu_ctd_qf)
s4 <- summary(as.factor(d$temp_fb_qf))*100/length(d$temp_fb_qf)
s5 <- summary(as.factor(d$temp_insitu_11m_qf))*100/length(d$temp_insitu_11m_qf)
# durafet and seafet started later
x <- filter(d, datetime >= as.POSIXct("2017-08-29 10:00:00"))
#s6 <- summary(as.factor(x$temp_dur_qf))*100/length(x$temp_dur_qf)
s7 <- summary(as.factor(x$ph_dur_qf))*100/length(x$ph_dur_qf)
x <- filter(d, datetime >= as.POSIXct("2017-08-24 19:00:00"))
s8 <- summary(as.factor(x$phINT_qf))*100/length(x$phINT_qf)
z <- t(bind_rows(s1,s2,s3,s4,s5,s7,s8)) %>%
  as.data.frame() %>%
         rownames_to_column(var = "flag") %>% 
         as_tibble()
labels <- c("Good", "Not usable", "Outside regional range", "Outliers (despike)", 
            "Failed visual inspection", "No data")
#colnames(z) <- c("flag", colnames(d)[-1]) # remove first col name (datetime)
colnames(z) <- c("Flag", "pCO2", "Salinity FerryBox", "In situ salinity", 
                 "Temperature FerryBox", "In situ temperature", "Durafet pH", "seaFET pH")
zz <- pivot_longer(z, -Flag)
p <-  ggplot(data = zz, aes(x = name, y = value, fill = Flag)) +
  geom_bar(position = position_stack(reverse = TRUE), stat="identity", width = 0.3) +
  #scale_y_reverse() +
  #discrete_scale(labels = labels) + 
  coord_flip() +
  geom_text(aes(label=round(value, digits = 0)), position = position_stack(0.5), size = 3) +
  labs(x="", y="", title = "Distribution (%) of quality flags", color = "Quality flag") +
  theme_bw()
p
rm(d)
```

@@

```{r figures for ESSD paper, echo=FALSE, message= FALSE, warning=FALSE}
Mytheme <- function(size_labs = 6, face_font="plain", ...) {
  theme_bw() +
  theme(
    # axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
    #     axis.title.x = element_text(face="plain", size=size_labs, margin=margin(0,0,0,0,"pt")),
    #     axis.text.y = element_text(face=face_font, color="black", size=size_labs),
    axis.text.x = element_blank(),
    #     axis.title.y = element_text(face="plain", size=size_labs),
    #     axis.ticks.x = element_line(size=0.1),
    #     axis.ticks.y = element_line(size=0.1),
    #     axis.ticks.length = unit(1.1, "mm"),
    #     panel.grid.major = element_line(size = 0.2, color="black", linetype="dotted"),
    #     aspect.ratio = 1 / 3,
        plot.margin = margin(t = 0, r = 0.3, b = 0, l = 0.3, unit = "cm")
  )
}
xlim <- c(as.POSIXct("2015-07-01 00:00:00"), as.POSIXct("2020-07-01 00:00:00"))
# select time series data
d <- as_tibble(d_all) %>%
  dplyr::select(datetime, temp_insitu_11m, sal_mix, pco2_corr, pHint_tot_sf, ph_dur_corr, at_calc)
# time series temp
ts_temp <- d %>%
  dplyr::filter(!is.na(temp_insitu_11m)) %>% 
  ggplot() +
  geom_point(aes(x = datetime, y = temp_insitu_11m), col = "blue", size = 0.15) +
  labs(title = "", x = "", y = "Temp. 11 m (°C)") +
  Mytheme(size_labs = 8)
print(ts_temp) 
# time series sal
ts_sal <- d %>%
  dplyr::filter(!is.na(sal_mix)) %>% 
ggplot() +
  geom_point(aes(x = datetime, y = sal_mix), col = "blue", size = 0.15) + 
  labs(title = "", x = "", y = "Salinity") +
  Mytheme(size_labs = 8)
print(ts_sal) 
# time series pco2
ts_pco2 <- d %>%
  dplyr::filter(!is.na(pco2_corr)) %>% 
  ggplot() +
  geom_point(aes(x = datetime, y = pco2_corr), col = "blue", size = 0.15) +
  scale_x_datetime(limits = xlim) +
  labs(title = "", x = "", y = expression(paste("pC", O[2], " (", mu, "atm)"))) +
  Mytheme(size_labs = 8)
print(ts_pco2) 
# time series pH
ts_ph <- d %>%
  dplyr::select(datetime, pHint_tot_sf, ph_dur_corr) %>%
  dplyr::filter(!is.na(pHint_tot_sf)) %>%
  pivot_longer(-datetime, names_to = "pH", values_to = "value") %>%
  ggplot() +
  geom_point(aes(x = datetime, y = value, colour = pH), size = 0.15) +
  scale_x_datetime(limits = xlim) +
  labs(title = "",
       x = "",
       y = expression(paste("p", H[T]))) +
  # scale_color_manual(
  #   values = c("blue", "red"),
  #   name = "",
  #   breaks = c("pHint_tot_sf", "ph_dur_corr"),
  #   labels = c("SeaFET", "Durafet")
  # ) +
  annotate(
    geom = "text",
    x = as.POSIXct("2018-06-01"),
    y = 8.35,
    label = "seaFET",
    color = "blue", size = 2
  ) +
  annotate(
    geom = "text",
    x = as.POSIXct("2018-06-01"),
    y = 8.25,
    label = "Durafet",
    color = "red", size = 2
  ) +
  Mytheme(size_labs = 8) +
  theme(legend.position = "none")
print(ts_ph) 
# time series AT
ts_at <- d %>%
  dplyr::filter(!is.na(at_calc)) %>% 
  ggplot() +
  geom_point(aes(x = datetime, y = at_calc), col = "blue", size = 0.15) +
  scale_x_datetime(limits = xlim) +
  labs(title = "", x = "Time", y = expression(paste(italic(A)[T]," ","(",mu, mol.kg^-1,")"))) +
  Mytheme(size_labs = 8) +
  theme(axis.title.x = element_text(face="plain", size=8))
print(ts_at)

@@

### Data processing
#### Script ny-alesund_cc.R which runs on awipev@awipev-co2.obs-vlfr.fr
* reads data from the AWI NRT database [Quick overview AWI NRT database](https://dashboard.awi.de/?dashboard=9736) 
* calibrates pCO2 data
* data cleaning:
  + Argo Global Range Test.
  + filter salinities above 28
  + filter temperatures above 10
  + filter seaFET Volt (outliers)
  + filter seaFET pH (outliers)
  + filter durafet (outliers)
* Quality flags
    + 1: good data
    + 3: impossible date and time test
    + 4: data not usable according to manufacturer (flush mode, zero mode, calibration mode...) 
    + 6: failing the manufacturer range test (not used)
    + 7: failing the regional range test 
    + 12: failing the spike test (NAs from despike)
    + 13: failing the gradient test
    + 15: the instrument was not deployed or operated
    + 99: failing the final visual inspection of the data. 
* Despike using oce::despike with n=2, k=5761
* Files generated:
    + previous_NRT_data.rds: all NRT data without alteration from the beginning (2015)
    + all_nydata_minute.rds: all data after filtering and despike describe above (every minute)
    + all_nydata_hour.rds: hourly means of all data after filtering and despike describe above (every minute)
    + nydata_minute.rds: selected data after filtering and despike describe above (every minute). **Useful?**
    + nydata_hour.rds: selected hourly means of all data after filtering and despike describe above (every minute).  This is for further data processing.

>>>>

+ 1: good data
+ 3: failing the date and time test
+ 4: data not usable according to manufacturer
+ 6: failing the manufacturer range test (not used)
+ 7: failing the regional range test 
+ 12: failing the spike test (NAs from despike)
+ 13: failing the gradient test
+ 15: instrument not deployed or operated
+ 16: acid flush
+ 99: failing the final visual inspection

@@

```{r data availability, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
d <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_minute.rds")) %>%
dplyr::select(datetime, c(pco2_corr_qf, sal_fb_qf, sal_insitu_ctd_qf, 
                          temp_fb_qf, temp_insitu_11m_qf, ph_dur_qf, phINT_qf))

s1 <- summary(as.factor(d$pco2_corr_qf))*100/length(d$pco2_corr_qf)
s2 <- summary(as.factor(d$sal_fb_qf))*100/length(d$sal_fb_qf)
s3 <- summary(as.factor(d$sal_insitu_ctd_qf))*100/length(d$sal_insitu_ctd_qf)
s4 <- summary(as.factor(d$temp_fb_qf))*100/length(d$temp_fb_qf)
s5 <- summary(as.factor(d$temp_insitu_11m_qf))*100/length(d$temp_insitu_11m_qf)
# durafet and seafet started later
x <- filter(d, datetime >= as.POSIXct("2017-08-29 10:00:00"))
#s6 <- summary(as.factor(x$temp_dur_qf))*100/length(x$temp_dur_qf)
s7 <- summary(as.factor(x$ph_dur_qf))*100/length(x$ph_dur_qf)
x <- filter(d, datetime >= as.POSIXct("2017-08-24 19:00:00"))
s8 <- summary(as.factor(x$phINT_qf))*100/length(x$phINT_qf)
z <- t(bind_rows(s1,s2,s3,s4,s5,s7,s8)) %>%
  as.data.frame() %>%
         rownames_to_column(var = "flag") %>% 
         as_tibble()
labels <- c("Good", "Not usable", "Outside regional range", "Outliers (despike)", 
            "Failed visual inspection", "Not deployed or operated", "Acid flush", "Failed visual inspection")
colnames(z) <- c("Flag", "pCO2", "Salinity FerryBox", "In situ salinity", 
                 "Temperature FerryBox", "In situ temperature", "Durafet pH", "seaFET pH")
zz <- pivot_longer(z, -Flag)
p <- ggplot(data = zz, aes(x = name, y = value, fill = Flag)) +
  geom_bar(position = position_stack(reverse = TRUE), stat="identity", width = 0.3) +
  #scale_y_reverse() +
  scale_fill_discrete(labels = labels) + 
  coord_flip() +
  #geom_text(aes(label=round(value, digits = 0)), position = position_stack((hjust = 0.5)), size = 3) +
  labs(x="", y="", title = "Distribution (%) of quality flags", color = "Quality flag") +
  Mytheme(size_labs = 8) +
  theme(plot.margin = margin(t = 0, r = 0.0, b = 0, l = 0.0, unit = "cm"))
ggsave(filename = "figures/availability.png", plot = p, width = 20, units = "cm")
kable(z, digits = 1)
rm(d)
```

@@

```{r figures for ESSD paper, echo=FALSE, message= FALSE, warning=FALSE}
Mytheme <- function(size_labs = 6, face_font="plain", ...) {
  theme_bw() +
  theme(
    # axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
    #     axis.title.x = element_text(face="plain", size=size_labs, margin=margin(0,0,0,0,"pt")),
    #     axis.text.y = element_text(face=face_font, color="black", size=size_labs),
    axis.text.x = element_blank(),
    #     axis.title.y = element_text(face="plain", size=size_labs),
    #     axis.ticks.x = element_line(size=0.1),
    #     axis.ticks.y = element_line(size=0.1),
    #     axis.ticks.length = unit(1.1, "mm"),
    #     panel.grid.major = element_line(size = 0.2, color="black", linetype="dotted"),
    #     aspect.ratio = 1 / 3,
        plot.margin = margin(t = 0, r = 0.3, b = 0, l = 0.3, unit = "cm")
  )
}

xlim <- c(as.POSIXct("2015-07-01 00:00:00"), as.POSIXct("2020-07-01 00:00:00"))
# select time series data
d <- as_tibble(d_all) %>%
  dplyr::select(datetime, temp_insitu_11m, sal_mix, pco2_corr, pHint_tot_sf, ph_dur_corr, at_calc)
# time series temp
ts_temp <- d %>%
  dplyr::filter(!is.na(temp_insitu_11m)) %>% 
  ggplot() +
  geom_point(aes(x = datetime, y = temp_insitu_11m), col = "blue", size = 0.15) +
  labs(title = "", x = "", y = "Temp. 11 m (°C)") +
  Mytheme(size_labs = 8)
print(ts_temp) 
# time series sal
ts_sal <- d %>%
  dplyr::filter(!is.na(sal_mix)) %>% 
ggplot() +
  geom_point(aes(x = datetime, y = sal_mix), col = "blue", size = 0.15) + 
  labs(title = "", x = "", y = "Salinity") +
  Mytheme(size_labs = 8)
print(ts_sal) 
# time series pco2
ts_pco2 <- d %>%
  dplyr::filter(!is.na(pco2_corr)) %>% 
  ggplot() +
  geom_point(aes(x = datetime, y = pco2_corr), col = "blue", size = 0.15) +
  scale_x_datetime(limits = xlim) +
  labs(title = "", x = "", y = expression(paste("pC", O[2], " (", mu, "atm)"))) +
  Mytheme(size_labs = 8)
print(ts_pco2) 
# time series pH
ts_ph <- d %>%
  dplyr::select(datetime, pHint_tot_sf, ph_dur_corr) %>%
  dplyr::filter(!is.na(pHint_tot_sf)) %>%
  pivot_longer(-datetime, names_to = "pH", values_to = "value") %>%
  ggplot() +
  geom_point(aes(x = datetime, y = value, colour = pH), size = 0.15) +
  scale_x_datetime(limits = xlim) +
  labs(title = "",
       x = "",
       y = expression(paste("p", H[T]))) +
  # scale_color_manual(
  #   values = c("blue", "red"),
  #   name = "",
  #   breaks = c("pHint_tot_sf", "ph_dur_corr"),
  #   labels = c("SeaFET", "Durafet")
  # ) +
  annotate(
    geom = "text",
    x = as.POSIXct("2018-06-01"),
    y = 8.35,
    label = "seaFET",
    color = "blue", size = 2
  ) +
  annotate(
    geom = "text",
    x = as.POSIXct("2018-06-01"),
    y = 8.25,
    label = "Durafet",
    color = "red", size = 2
  ) +
  Mytheme(size_labs = 8) +
  theme(legend.position = "none")
print(ts_ph) 
# time series AT
ts_at <- d %>%
  dplyr::filter(!is.na(at_calc)) %>% 
  ggplot() +
  geom_point(aes(x = datetime, y = at_calc), col = "blue", size = 0.15) +
  scale_x_datetime(limits = xlim) +
  labs(title = "", x = "Time", y = expression(paste(italic(A)[T]," ","(",mu, mol.kg^-1,")"))) +
  Mytheme(size_labs = 8) +
  theme(axis.title.x = element_text(face="plain", size=8))
print(ts_at)

@@

### Data processing
#### Script ny-alesund_cc.R which runs on awipev@awipev-co2.obs-vlfr.fr
* reads data from the AWI NRT database [Quick overview AWI NRT database](https://dashboard.awi.de/?dashboard=9736) 
* calibrates pCO2 data
* data cleaning:
  + Argo Global Range Test.
  + filter salinities above 28
  + filter temperatures above 10
  + filter seaFET Volt (outliers)
  + filter seaFET pH (outliers)
  + filter durafet (outliers)
* Quality flags
    + 1: good data
    + 3: impossible date and time test
    + 4: data not usable according to manufacturer (flush mode, zero mode, calibration mode...) 
    + 6: failing the manufacturer range test (not used)
    + 7: failing the regional range test 
    + 12: failing the spike test (NAs from despike)
    + 13: failing the gradient test
    + 15: the instrument was not deployed or operated
    + 16: acid flush
    + 99: failing the final visual inspection of the data. 
* Despike using oce::despike with n=2, k=5761
* Files generated:
    + previous_NRT_data.rds: all NRT data without alteration from the beginning (2015)
    + all_nydata_minute.rds: all data after filtering and despike describe above (every minute)
    + all_nydata_hour.rds: hourly means of all data after filtering and despike describe above (every minute)
    + nydata_minute.rds: selected data after filtering and despike describe above (every minute). **Useful?**
    + nydata_hour.rds: selected hourly means of all data after filtering and despike describe above (every minute).  This is for further data processing.
